Cost- and Deadline-Constrained Provisioning for Scientific Workflow Ensembles in IaaS Clouds

### 2012-07-25 paper/paper.tex
Add STCI acknowlegement
improved Fig. 1

DPDS guarantees that tasks from lower priority workflows are always deferred
when higher-priority tasks are available, but lower-priority tasks can still
occupy idle VMs when higher-priority tasks are not available. Since there is
no preemption, long-running low-priority tasks may delay the execution of
higher-priority tasks. In addition, tasks from low priority workflows may be
executed even though there is no chance that those workflows will be completed
within the current budget and deadline. Fig.~\ref{fig:algorithm-example}a
shows an example schedule generated using the DPDS algorithm. The figure
illustrates how tasks from lower priority workflows backfill idle VMs when
tasks from higher priority workflows are not available.

@@

\begin{figure}[tb] 
  \centering
  \subfloat[DPDS]{
  \includegraphics[width=0.40\textwidth]{figures/spds-gantt}
  }\\
  \subfloat[SPSS]{
  \includegraphics[width=0.40\textwidth]{figures/spss-gantt}
  }
  \caption[Example schedules generated by the algorithms]{Example
  schedules generated by the algorithms. Each row is a different
  VM. Boxes are tasks colored by workflow.}
  \label{fig:algorithm-example}
\end{figure}

An example schedule generated by SPSS (Fig.~\ref{fig:algorithm-example}b)
shows how SPSS tends to start many workflows in parallel, running each workflow
over a longer period of time on only a few VMs to minimize cost. In comparison,
the dynamic algorithms tend to run one workflow at a time across many VMs in
parallel.

@@

\begin{figure*}[tb]
    \subfloat[Ratio of Simulated Ensemble Cost to Budget]{
        \includegraphics[width=0.4\textwidth]{run-finish-failures-test-0-output-cost-all}
    }
    \hspace{2cm}
    \subfloat[Ratio of Simulated Ensemble Makespan to Deadline]{
        \includegraphics[width=0.4\textwidth]{run-finish-failures-test-0-output-makespan-all}
    }
    \caption{Boxplots for budget and deadline ratios when failure rate varies
    from 0\% to 50\% for all three algorithms. Values greater than 1 indicate 
    that the budget/deadline constraint was exceeded.}
    \label{fig:failures}
\end{figure*}

@@

\begin{figure}[tb]
    \centering
    \vspace{-6mm}
    \includegraphics[width=0.30\textwidth]{spss_planning_time}
    \vspace{-3mm}
    \caption{Planning time of SPSS algorithm for ensembles of 100 workflows and different workflow sizes.}
    \label{fig:spss_planning_time}
\end{figure}

@@

%\section*{Acknowledgments}
%Acknowledgements go here.

>>>>

DPDS guarantees that tasks from lower priority workflows are always deferred
when higher-priority tasks are available, but lower-priority tasks can still
occupy idle VMs when higher-priority tasks are not available. Since there is
no preemption, long-running low-priority tasks may delay the execution of
higher-priority tasks. In addition, tasks from low priority workflows may be
executed even though there is no chance that those workflows will be completed
within the current budget and deadline. Fig.~\ref{fig:algorithm-example-dpds}
shows an example schedule generated using the DPDS algorithm. The figure
illustrates how tasks from lower priority workflows backfill idle VMs when
tasks from higher priority workflows are not available.

@@

\begin{figure}[tb] 
  \centering
  \subfloat[DPDS]{
  \includegraphics[width=0.40\textwidth]{figures/output-test-DPDS}
  \label{fig:algorithm-example-dpds}
  }\\
  \subfloat[SPSS]{
  \includegraphics[width=0.40\textwidth]{figures/output-test-SPSS}
  \label{fig:algorithm-example-spss}
  }
  \caption[Example schedules generated by the algorithms]{Example
  schedules generated by the algorithms. Each row is a different
  VM. Boxes are tasks colored by workflow.}

\end{figure}

An example schedule generated by SPSS (Fig.~\ref{fig:algorithm-example-spss})
shows how SPSS tends to start many workflows in parallel, running each workflow
over a longer period of time on only a few VMs to minimize cost. In comparison,
the dynamic algorithms tend to run one workflow at a time across many VMs in
parallel.

@@

\begin{figure*}[tb]
    \subfloat[Ratio of Simulated Ensemble Cost to Budget]{
        \includegraphics[width=0.38\textwidth]{run-finish-failures-test-0-output-cost-all}
        }
    \hspace{2cm}
    \subfloat[Ratio of Simulated Ensemble Makespan to Deadline]{
        \includegraphics[width=0.38\textwidth]{run-finish-failures-test-0-output-makespan-all}
        }
    \caption{Boxplots for budget and deadline ratios when failure rate varies
    from 0\% to 50\% for all three algorithms. Values greater than 1 indicate 
    that the budget/deadline constraint was exceeded.}
    \label{fig:failures}
\end{figure*}

@@

\begin{figure}[tb]
    \centering
    \vspace{-6mm}
    \includegraphics[width=0.27\textwidth]{spss_planning_time}
    \vspace{-3mm}
    \caption{Planning time of SPSS algorithm for ensembles of 100 workflows and different workflow sizes.}
    \label{fig:spss_planning_time}
\end{figure}

@@

\section*{Acknowledgments}
This work was sponsored by the National Science Foundation under award 
OCI-0943725 (STCI).
